sem

### 2022-12-09 scripts/workshop/sem.Rmd
log transform variables

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(cc ~ MeanWaterTempPredC, data = comm_data)
size_temp <- glm(size ~ MeanWaterTempPredC, data = comm_data)
prev_cc <- glm(Prevalence ~ cc + MeanWaterTempPredC + size, data = comm_data)

>>>>

histograms
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=size)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(size))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=cc)) + geom_histogram()
comm_data %>% ggplot(.,aes(x=log10(cc))) + geom_histogram()
comm_data %>% ggplot(.,aes(x=Prevalence)) + geom_histogram()
```
plots
```{r}
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(cc))) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = log10(size))) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=MeanWaterTempPredC, y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(cc), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
comm_data %>% ggplot(.,aes(x=log10(size), y = Prevalence)) + geom_point() + geom_smooth(method = "lm")
```

cc ~ mean water temp; size ~ mean water temp; prevalence ~ cc + size + mean water temp
```{r}
cc_temp <- glm(log10(cc) ~ MeanWaterTempPredC, data = comm_data)
size_temp <- glm(log10(size) ~ MeanWaterTempPredC, data = comm_data)
prev_cc <- glm(Prevalence ~ log10(cc) + MeanWaterTempPredC + log10(size), data = comm_data)
